FictionEro2 - Affective Impact of Fiction

### 2025-04-30 study2/analysis/2_emotion.qmd
updated script

df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, SexualActivity,
           -Feedback_Text),
    by = "Participant"
    ) |> 
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         GenderualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0 ~ "True",
           Condition == "AI-Generated" & Realness < 0 ~ "True",
           .default = "False",
         )) |>
  mutate(across(starts_with("Feedback_")& !matches("Feedback_AllRealConfidence|Feedback_AllFakeConfidence|Feedback_Enjoyment"), function(x) {fct_relevel(x, "False", "True")}))

@@

@@

@@

```{r}
test_moderator <- function(df, outcome="Arousal", moderator="Bait_Visual") {
  f <- paste0(outcome, " ~ Gender / (Condition * ", moderator, ") + (Condition | Participant) + (1|Stimulus)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data = df,
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  r$Outcome <- outcome
  insight::format_table(r[c(7, 8), ])
}

moderator_results <- data.frame()
for(m in c("BAIT_VideosRealistic", "BAIT_TextRealistic", "BAIT_ExpertAI", "PornFrequency", "SexualActivity")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Arousal", m))
}

@@

>>>>

df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity, BAIT_Worry, BAIT_Dangerous, 
           -Feedback_Text),
    by = "Participant"
    ) |> 
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexurualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0 ~ "True",
           Condition == "AI-Generated" & Realness < 0 ~ "True",
           .default = "False",
         )) |>
  mutate(across(starts_with("Feedback_")& !matches("Feedback_AllRealConfidence|Feedback_AllFakeConfidence|Feedback_Enjoyment"), function(x) {fct_relevel(x, "False", "True")}))

@@

**Note**: [These calculations are based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)

bait <- df |> 
  select(starts_with("BAIT_"), -Bait_Duration) |> 
  rename_with(function(x) gsub("BAIT_\\d_", "", x)) |> 
  filter(!is.na(BAIT_TextRealistic ))

raw_scores <- data.frame(
  Participant = df[!is.na(df$BAIT_ImagesRealistic), ]$Participant,
  BAIT_Videos = (bait$BAIT_VideosRealistic + (1 - bait$BAIT_VideosIssues)) / 2,
  BAIT_Visual = (bait$BAIT_ImagesRealistic + (1 - bait$BAIT_ImagesIssues) + bait$BAIT_ImitatingReality + bait$BAIT_EnvironmentReal) / 4,
  BAIT_Text = (bait$BAIT_TextRealistic + (1 - bait$BAIT_TextIssues)) / 2
  )

df <- merge(df, raw_scores, by="Participant")
```

@@

```{r}
estimate_relation(m_v) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

@@

```{r}
test_moderator <- function(df, outcome="Arousal", moderator="BAIT_Visual") {
  f <- paste0(outcome, " ~ Gender / (Condition * ", moderator, ") + (Condition | Participant) + (1|Stimulus)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data = df,
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  r$Outcome <- outcome
  insight::format_table(r[c(7, 8), ])
}

moderator_results <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI", "PornFrequency", "SexualActivity")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Arousal", m))
}

@@

### Believed

```{r}
  m <- glmmTMB::glmmTMB(Arousal ~ Sex / Condition + (1|Participant) + (1|Item),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

  results_table(m)
```

 moderator_believed <- data.frame()
  for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
             "GAAIS_Positive", "GAAIS_Negative",
             "Porn", "PornFrequency", "SexualActivity_num", 
             "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
             "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
             "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
    moderator_believed <- rbind(moderator_believed,
                               test_moderator(filter(df, ConditionBelief == "True"), "Arousal", m))
  }

  display(filter(moderator_believed, p < .1))
